---
title: "Housing Cost Prediction Project"
author: 'Jingyi Zhao'
date: "10/05/2022"
output: 
  pdf_document:
    latex_engine: xelatex
    extra_dependencies: ["fontspec"]
    keep_tex: true
    fig_caption: true
    fig_width: 6
    fig_height: 4
    dpi: 72
---
Using the data set kc_house_data.csv, build a model to predict housing cost. 
```{r}
knitr::opts_chunk$set(
  echo = TRUE,
  fig.width = 6,
  fig.height = 4,
  dpi = 72,
  dev = 'cairo_pdf'
)

```

```{r}
setwd("/Users/zhaojingyi/MAS432")
df=read.csv("kc_house_data.csv")
summary(df)
```
```{r results= "hide"}
library(leaps)
BSR = regsubsets(price~bedrooms+bathrooms+sqft_living+sqft_lot+floors+waterfront+view+condition+grade+sqft_above+sqft_basement+yr_built+yr_renovated+zipcode+lat+long+sqft_living15+sqft_lot15, data =df)
plot(BSR)
plot(BSR, scale = "adjr2")
```
Which variables are in the best subset?
*bedrooms, sqft_living, waterfront, view, grade,yr_renovated, lat, long, sqft_living15*

Use R to the find the number of variables in best subsets.
```{r}
s= summary(BSR)
#s$adjr2
which.max(s$adjr2)
```
Get a summary of the best subsets result.
```{r}
reg=lm(price~bedrooms+sqft_living+ waterfront+view+grade+yr_renovated+lat+long+sqft_living15,data=df)
summary(reg)
```
```{r}
df1= subset(df, select=c('bedrooms', 'sqft_living', 'waterfront', 'view', 'grade','yr_renovated', 'lat', 'long', 'sqft_living15'))
```
Find a correlation plot between the variables within the data subset(bedrooms, sqft_living, waterfront, view, grade,yr_renovated, lat, long, sqft_living15)
```{r}
library(corrplot)          
M<-cor(df1)
c=cor(M)
corrplot(M)
```


#Generate a scatterplot matrix from the variables within the data subset
```{r}
plot(df1)
```


```{r}
barplot(df$bedrooms, xlab = "bedrooms", ylab = "Frequency",
main = "Barplot of symboling Frequencies")
barplot(df$sqft_living, xlab = "sqft_living", ylab = "Frequency",
main = "Barplot of symboling Frequencies")
barplot(df$waterfront, xlab = "waterfront", ylab = "Frequency",
main = "Barplot of symboling Frequencies")
barplot(df$view, xlab = "view", ylab = "Frequency",
main = "Barplot of symboling Frequencies")
barplot(df$grade, xlab = "grade", ylab = "Frequency",
main = "Barplot of symboling Frequencies")
barplot(df$yr_renovated, xlab = "yr_renovated", ylab = "Frequency",
main = "Barplot of symboling Frequencies")
barplot(df$lat, xlab = "lat", ylab = "Frequency",
main = "Barplot of symboling Frequencies")
barplot(df$long, xlab = "long", ylab = "Frequency",
main = "Barplot of symboling Frequencies")
barplot(df$sqft_living15, xlab = "sqft_living15", ylab = "Frequency",
main = "Barplot of symboling Frequencies")
```

## Construct a scatterplot and histogram of the residuals for the Full model
```{r}
plot(reg,which=1)
hist(reg$residuals, xlab = "Residuals")
library(car)
boxCox(reg)
```
Since lambda is nearest to 0, use log to transfrom
## BoxCox (Response variable transformation)
```{r}
regnew = lm(log(price)~bedrooms+sqft_living+ waterfront+view+grade+yr_renovated+lat+long+sqft_living15,data=df)
summary(regnew)
```
#Checking normality
```{r}
library(ggplot2)
par(mfrow= c(2,2))
qqnorm(df$bedrooms)
qqline(df$bedrooms)
qqnorm(df$sqft_living)
qqline(df$sqft_living)
qqnorm(df$waterfront)
qqline(df$waterfront)
qqnorm(df$view)
qqline(df$view)
qqnorm(df$grade)
qqline(df$grade)
qqnorm(df$yr_renovated)
qqline(df$yr_renovated)
qqnorm(df$lat)
qqline(df$lat)
qqnorm(df$long)
qqline(df$long)
qqnorm(df$sqft_living15)
qqline(df$sqft_living15)
```
#Comparison with original and tranformed
```{r results= "hide"}
par(mfrow= c(2,2))
hist(df$bedrooms, main = "Histogram of (bedrooms)", xlab = "(bedrooms)")
hist(log(df$bedrooms), main = "Histogram of log(bedrooms)", xlab = "log(bedrooms)") 
hist(df$sqft_living, main = "Histogram of (sqft_living)", xlab = "(sqft_living)")
hist(log(df$sqft_living), main = "Histogram of log(sqft_living)", xlab = "log(sqft_living)") 
hist(df$waterfront, main = "Histogram of (waterfront)", xlab = "(waterfront)")
hist(log(df$waterfront), main = "Histogram of log(waterfront)", xlab = "log(waterfront)") 
hist(df$view, main = "Histogram of (view)", xlab = "(view)")
hist(log(df$view), main = "Histogram of log(view)", xlab = "log(view)") 
hist(df$grade, main = "Histogram of (grade)", xlab = "(grade)")
hist(log(df$grade), main = "Histogram of log(grade)", xlab = "log(grade)") 
hist(df$yr_renovated, main = "Histogram of (yr_renovated)", xlab = "(yr_renovated)")
hist(log(df$yr_renovated), main = "Histogram of log(yr_renovatedt)", xlab = "log(yr_renovated)") 
hist(df$lat, main = "Histogram of (lat)", xlab = "(lat)")
hist(log(df$lat), main = "Histogram of log(lat)", xlab = "log(lat)")
hist(df$sqft_living15, main = "Histogram of (sqft_living15)", xlab = "(sqft_living15)")
hist(log(df$sqft_living15), main = "Histogram of log(sqft_living15)", xlab = "log(sqft_living15)")
```


```{r}
cooks<-cooks.distance(regnew)
plot(cooks,main="cook's distance for price")
```

```{r}
regnew2 = lm(log(df$price) ~bedrooms+sqft_living+ waterfront+view+grade+yr_renovated+lat+long+sqft_living15 , data = df)
summary(regnew2)
```
```{r}
par(mfrow= c(2,2))
reg1=lm(price~bedrooms,data=df)
plot(reg1,which=1)
plot(price~bedrooms,data=df)
abline(reg1, col = "red")
reg2=lm(price~sqft_living,data=df)
plot(reg2,which=1)
plot(price~sqft_living,data=df)
abline(reg2, col = "red")
reg3=lm(price~waterfront,data=df)
plot(reg3,which=1)
plot(price~waterfront,data=df)
abline(reg3, col = "red")
reg4=lm(price~view,data=df)
plot(reg4,which=1)
plot(price~view,data=df)
abline(reg4, col = "red")
reg5=lm(price~grade,data=df)
plot(reg5,which=1)
plot(price~grade,data=df)
abline(reg5, col = "red")
reg6=lm(price~yr_renovated,data=df)
plot(reg6,which=1)
plot(price~yr_renovated,data=df)
abline(reg6, col = "red")
reg7=lm(price~lat,data=df)
plot(reg7,which=1)
plot(price~lat,data=df)
abline(reg7, col = "red")
reg8=lm(price~long,data=df)
plot(reg8,which=1)
plot(price~long,data=df)
abline(reg8, col = "red")
reg9=lm(price~sqft_living15,data=df)
plot(reg9,which=1)
plot(price~sqft_living15,data=df)
abline(reg9, col = "red")
```
```{r}
knitr::opts_chunk$set(dev = 'cairo_pdf')
```
```{r}
compress_pdf <- function(input_file, output_file) {
  gs_cmd <- sprintf(
    "gs -sDEVICE=pdfwrite -dCompatibilityLevel=1.4 -dPDFSETTINGS=/screen -dNOPAUSE -dQUIET -dBATCH -sOutputFile=%s %s",
    output_file, input_file
  )
  system(gs_cmd)
}

# Compress the knitted PDF
compress_pdf("FinalProject.pdf", "FinalProject_compressed.pdf")

```

